Analyzing X-ray images in Python with scikit-image

### 2016-08-25 skimage_tomo.tex
Add suggestions for deficiencies section

\texttt{scikit-image} is developed by a diverse team of volunteers.
More than 170 individuals have contributed to the package. The large
number of developers and users is a key element of the sustainability of
\texttt{scikit-image}. The
development process takes place on GitHub
\url{https://github.com/scikit-image/scikit-image}, where users and
developers propose and discuss new contributions, report bugs or submit ideas
for improvements.
A release cycle of one or two releases every year
ensures that new features are propagated to users on a regular basis.

@@

While we have insisted on the assets of \texttt{scikit-image} for processing
X-ray images, one should be aware of current limitations of the package.

\paragraph{Speed of execution.} Although \texttt{scikit-image} approaches
the speed of execution of compiled (C++, Java) code, it cannot reach the
performance of code optimized for the GPU. At the moment,
\texttt{scikit-image} is not the best tool for ultrafast computations
where the workflow is known beforehand, simple and stable. However, it is
an excellent tool for exploring image data interactively and testing
different algorithms -- an important component of data processing in
scientific work --, and its speed of execution is good enough to process
gigabyte-sized tomographic images in seconds to minutes. Moreover,
the multiprocessing capability of \texttt{scikit-image} should improve in
the near future.

\paragraph{3-D compatibility.} At the moment, about two thirds of
\texttt{scikit-image} functions transparently handle 2D or 3D arrays, with
the remainder limited to 2D analysis, often unnecessarily. Improved support
for 3D and higher-dimensional volumes is in the project roadmap, however.

\paragraph{Documentation for domain-specific applications.} Some image
processing libraries or applications address a specific scientific
domain, such as CellProfiler \citep{Carpenter2006, Lamprecht2007} for
biological images. The documentation of such projects often showcases
examples that are close to the experience of the targeted community.
Since \texttt{scikit-image} is application-agnostic,
applications such as tomographic imaging are not mentioned in detail in the
documentation of \texttt{scikit-image}. A possible improvement would be
to write comprehensive tutorials addressing specific communities, and to
reference these tutorials from the main \texttt{scikit-image}
documentation.

@@

Scientists interested in experimenting with \texttt{scikit-image} are
invited to read the installation instructions on
\url{http://scikit-image.org/docs/stable/install.html}.
\texttt{scikit-image} can be installed either bundled in a Scientific
Python distribution, such as Anaconda or Canopy, or alone (with its
dependencies) using a installer/packager program such as pip or Ubuntu's
Synaptic.

The Getting started section of the online User Guide
(\url{http://scikit-image.org/docs/dev/user_guide/getting_started.html})
is a good starting point, as well as the other sections of the user
guide. Examples of the gallery
(\url{http://scikit-image.org/docs/dev/auto_examples/}) can be used to
find applications close to one's needs. Although most examples of the
gallery use 2D images, most functions can be used with 3D images as well.

Assistance on matters not covered by the documentation is provided to
users either on the dedicated mailing-list
\url{scikit-image@googlegroups.com} or on StackOverflow
\url{http://stackexchange.com/filters/87964/scikit-image}.

>>>>

\texttt{scikit-image} is developed by a diverse team of volunteers.
More than 170 individuals have contributed to the package. The large
number of developers and users key to project's sustainability. The
development process takes place on GitHub
\url{https://github.com/scikit-image/scikit-image}, where users and
developers propose and discuss new contributions, report bugs or submit ideas
for improvements.
A release cycle of one or two releases every year
ensures that new features are propagated to users on a regular basis.

@@

While we emphasize the assets of \texttt{scikit-image} for processing
X-ray images, one should be aware of current limitations.

\paragraph{Speed of execution.} Although \texttt{scikit-image} approaches
the speed of execution of compiled (C++, Java) code, it cannot reach the
performance of code optimized for the GPU, or the hand-tuned
CPU-specific optimizations found in OpenCV. At the moment,
\texttt{scikit-image} is not the best tool for ultrafast computations
where the workflow is known beforehand, simple and stable. However, it is
an excellent tool for exploring image data interactively and testing
different algorithms -- an important component of data processing in
scientific work --, and its speed of execution is sufficient for processing
gigabyte-sized tomographic images in seconds to minutes. Moreover,
the multiprocessing capability of \texttt{scikit-image} is likely to improve in
the near future.

\paragraph{3-D compatibility.} Currently, about two thirds of
\texttt{scikit-image} functions transparently handle 2D or 3D arrays, with
the remainder limited to 2D analysis, often unnecessarily. Improved support
for 3D and higher-dimensional volumes is on the project roadmap.

\paragraph{Documentation for domain-specific applications.} Some image
processing libraries or applications address a specific scientific
domain, such as CellProfiler \citep{Carpenter2006, Lamprecht2007} for
biological images. The documentation of such projects often showcases
examples that are close to the experience of the targeted community.
Since \texttt{scikit-image} is application-agnostic,
applications such as tomographic imaging are not mentioned in detail in the
documentation of \texttt{scikit-image}. A possible improvement would be
to write comprehensive tutorials addressing specific communities, and to
refer to these tutorials from the main \texttt{scikit-image}
documentation.

@@

Scientists interested in experimenting with \texttt{scikit-image} are
invited to read the installation instructions at
\url{http://scikit-image.org/docs/stable/install.html}.
\texttt{scikit-image} can be installed either bundled in a Scientific
Python distribution, such as Anaconda or Canopy, or stand alone (along with its
dependencies) using an installer/packager such as pip or Ubuntu's
Aptitude.

The Getting Started section of the online User Guide
(\url{http://scikit-image.org/docs/dev/user_guide/getting_started.html})
provides a good launch pad for beginners, and gently leads into other sections of the user
guide. A gallery of examples
(\url{http://scikit-image.org/docs/dev/auto_examples/}) lets users
find applications close to their needs. Although most examples in the
gallery use 2D images, many are applicable to 3D images as well.

Assistance on matters not covered by the documentation is provided on
the dedicated mailing-list \url{scikit-image@googlegroups.com} or on
StackOverflow
\url{http://stackoverflow.com/questions/tagged/scikit-image}.
